\begin{objectives}
    In this tutorial you will be exploring parametric equations.
\end{objectives}

\begin{enumerate}
    \item Consider a particle following a \emph{Lissajous curve} trajectory that is given by the parametric equations
    \[
    \begin{cases}
        x=\sin{4t}\\
        y=\sin{3t}
    \end{cases}\qquad 0 \leq t \leq 2\pi
    \]

    \begin{enumerate}
        \item Consider the derivatives $\frac{dx}{dt}$ and $\frac{dy}{dt}$. 
        When the particle is moving left, what must be true about $\frac{dx}{dt}$ and $\frac{dy}{dt}$?
        How about when the particle is moving right? Up? Down?

        \item Find a $t$ when the instantaneous velocity of the particle is moving diagonal, with a trajectory towards the upper left. Justify your answer.

        \item Find \textbf{all times} $t$ during which the particle is moving
        to the upper left.
        
    \end{enumerate}

    \item Consider the following curves given by parametric equations.

    \begin{tcolorbox}[sharp corners=all,colframe=tolGrey,colback=white]
    \begin{multicols}{2}
    \begin{enumerate}[label={(\roman{enumii})},nosep,itemsep=1mm]
        \item $x = \cos{2t}, y = \sin{2t}, 0 \leq t \leq \pi$
        \item $x = \cos{t}, y = \sin{t}, 0 \leq t \leq 2\pi$
        \item $x = \sin{t}, y = \cos{t}, 0 \leq t \leq 2\pi$
        \item $x = \cos{2t}, y = \cos{2t}, 0 \leq t \leq \pi$
        \item $x = \cos{t}, y = \sin{t}, 0 \leq t \leq \pi$
    \end{enumerate}
    \end{multicols}
    \end{tcolorbox}
    
    \begin{enumerate}
        \item Sketch the graph (by hand) of each set of parametric equations.
        Add arrows to your sketches to signify which direction each curve is traced out.

        \item Which parametric equations produce the same shapes when plotted in an $xy$-coordinate system? 
        
        Justify your answer by plotting in Desmos
        
        \url{https://www.desmos.com/calculator/24kii8joui}

        Note: \emph{make sure to appropriately adjust the domains of the parametric curves when you plot in Desmos.}
        
    \end{enumerate}

    % \item Consider constants $a,b,c,d$ such that $a^2+c^2 = b^2+d^2 = R^2$ and $ab+cd=0$. Show that the parametric equations below describe a circle of radius $R$.
    % \[
    %     \begin{cases}
    %     x = a\cos{t} + b\sin{t}\\
    %     y = c\cos{t} + d\sin{t}
    %     \end{cases}
    % \]

    \item A colony of ants is marching according to the trajectory $x(t) = \cos{t}, y(t)=\sin{3t}$. 
    \begin{enumerate}
    \item Graph $t$ vs.{} $x$ and $t$ vs.{} $y$.
    \item  Use your plots from part (a) to sketch the
    graph of $(x(t),y(t))$ for $t\in \R$.

    Verify your sketch using Desmos.

    \item Is there a tangent line to the graph at $(1/2,0)$ Why or why not?

    \item If we restrict the domain of $(x(t),y(t))$ to $t\in[0,\pi]$ is
    there a tangent line to the graph at $(1/2,0)$? If so, find it.
    
    \item If we restrict the domain of $(x(t),y(t))$ to $t\in[\pi,2\pi]$ is
    there a tangent line to the graph at $(1/2,0)$? If so, find it.

    \end{enumerate}
    
\end{enumerate}